A Large-scale Study of Polymorphism in R

### 2019-03-18 paper/main.tex
sec2

>>>>

\subsection{Types of Data}

Before attempting to define a type system for R, we should understand the
different kinds of values that programs operate on.  As we will see
different notions of type may emerge depending on how granular we want to
be.

The first distinction that can be made is based on the value of the
\code{typeof} function.  This function, given a value, will return one of
the following types: \code{logical} (vector of booleans), \code{integer}
(vector of integers), \code{double} (vector of floating points),
\code{complex} (vector of complex numbers), \code{character} (vector of
character strings), \code{raw} (vector of bytes) and \code{list}
(polymorphic vector), \x`code{NULL} (vector of NULL),
\code{closure} (function), \code{environment} (naming environment),
\code{S4} (S4 object) and others that are used within the implementation of
R (\code{special}, \code{builtin}, \code{symbol}, \code{pairlist},
\code{promise}, \code{language}, \code{char}, \code{...}, \code{any},
\code{expression}, \code{externalptr}, \code{bytecode} and \code{weakref}).

%% TODO : make the types all bold.

attributes:

  - dim

class:
